Online (Bandit) Policy Selection for EASY-Backfilling

### 2017-03-30 paper/paper.tex
fix denischanges

While parallel job scheduling is a old studied theoretical
problem~\cite{leung2004handbook} \texbf{PREFER DROZDOWSKI HERE + SURVEY 
FEITELSON-RUDOLPH-SWIEGELSHON}, the practical ramifications, varying
hypotheses, and inherent uncertainty of the problem applied on the HPC 
field have driven
practitioners to use \textit{simple} heuristics (and researchers to 
study their behavior).
The two most popular heuristics for HPC platforms are EASY~\cite{easy} and
Conservative~\cite{Mu'alem:2001:UPW:380314.380315} backfillings.

>>>>

While parallel job scheduling is a old studied theoretical
problem~\cite{leung2004handbook} \textbf{PREFER DROZDOWSKI HERE + SURVEY 
FEITELSON-RUDOLPH-SWIEGELSHON}, the practical ramifications, varying
hypotheses, and inherent uncertainty of the problem applied on the HPC 
field have driven
practitioners to use \textit{simple} heuristics (and researchers to 
study their behavior).
The two most popular heuristics for HPC platforms are EASY~\cite{easy} and
Conservative~\cite{Mu'alem:2001:UPW:380314.380315} backfillings.
